---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statart

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/statart)](https://CRAN.R-project.org/package=statart)
[![R-CMD-check](https://github.com/socimh/statart/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/socimh/statart/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The primary goal of statart is to migrate some useful commands (functions) from Stata to R. In terms of certain jobs, however, functions in `statart` may perform better than any existing functions in Stata or R.

These functions are built in the tidyverse framework, including

- `codebook()` for codebook (like `codebook` in Stata)
- `summ()` for summary statistics (like `summarize` in Stata)
- `tab()`, `tab1()`, and `tab2()` for frequency tables (like `tab`, `tab1`, and `tab2` in Stata)
- `fre()`, `fre1()`, and `fre2()` for frequency tables with total rows and total columns (like `fre` in Stata)

## Installation

You can install the development version of statart like so:

```r
devtools::install_github("socimh/statart")
```

## Example

### Load the package

I highly recommend using `tidyverse` with `statart` for better performance.

```{r, warning=FALSE, message=FALSE}
library(statart)
library(tidyverse)
```

### codebook()

View the codebook of `lifeexp`.

```{r}
codebook(lifeexp)
```

### summ()

Summarise the numeric variables in `lifeexp`.

```{r, error=TRUE}
summ(lifeexp)
```

Not that `region` is a factor variable, so the mean and standard deviation of it may be meaningless.

### tab()

Tabulate a single variable:

```{r}
tab(starwars, sex)
```

`s_match()` can select variables in a stata style.

```{r}
tab(starwars, s_match("*color")) 
```

`tab1()` tabulates variables one by one as a list.

```{r}
tab1(starwars, s_match("*color"))
```

`.append` can flatten the list into a tibble.

```{r}
tab1(starwars, s_match("*color"), .append = TRUE)
```

`tab2()` cross-tabulates two variables.

```{r}
tab2(starwars, s_match("*i*color"))
```


### fre()

`fre()` family functions simply add total rows (and total columns in `fre2()`) to their `tab()` counterparts.

```{r}
fre(starwars, sex)
```

As the “Total” row is added, subsequent analysis on the result becomes more complicated, and the categories of the variable will be always converted to `character` (i.e., the same type as “Total”). However, I still keep these functions as they print the results with more comprehensive information.


### s_...() tools

"s" stands for `statart` as "st_" has already be taken by the powerful geospatial package `sf`. Let me briefly introduce some of them here.

`s_select()` extends the `select()` in tidyverse to enable data-masking features. For example,

```{r}
starwars %>%
  s_select(tall_characters = height > 100)
```

If you do not know whether a function works without any error, you could use `s_try()`.

```{r, error=TRUE}
starwars %>%
  select(tall_characters = height > 100) %>%
  s_try()

starwars %>%
  s_select(tall_characters = height > 100) %>%
  s_try()
```

Built on `pillar::type_sum()` and `vctrs::vec_ptype_abbr()`, `s_type()` returns the type of input object.

```{r}
s_type(lifeexp)

s_type(lifeexp$region)
```

`s_print()` is designed for viewing long data by their top and bottom rows.  

```{r, error=TRUE}
s_print(lifeexp)

lifeexp %>%
  fre(safewater) %>%
  s_print()
```

`s_time()` shows the time spent on running a function:  

```{r}
summ_result <- lifeexp %>%
  summ() %>%
  s_time()
```

... and it does not affect the function result.

```{r}
summ_result
```

## Code of Conduct

Please note that the statart project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
