---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Packages

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/Packages)](https://CRAN.R-project.org/package=Packages)
<!-- badges: end -->

The primary goal of statart is to migrate some useful commands (functions) from Stata to R. Functions are built in the tidyverse framework, including
- `tab()` and `tab1()` for frequency tables (like `tab` and `tab1` in Stata)
- `fre()` for frequency tables with missing information (like `fre` in Stata)
- `summ()` for summary statistics (like `summarize` in Stata)
- `codebook()` for codebook (like `codebook` in Stata)

## Installation

You can install the development version of Packages like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(startart)

codebook(mtcars)
```
