---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statart

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/statart)](https://CRAN.R-project.org/package=statart)
[![R-CMD-check](https://github.com/socimh/statart/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/socimh/statart/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

[statart](https://socimh.github.io/statart/) is a set of functions that combines Stata-inspired features with tidyverse-style operations. Find out more in the vignette("statart").

<!-- These functions are built in the tidyverse framework, including

- `codebook()` for codebook (like `codebook` in Stata)
- `summ()` for summary statistics (like `summarize` in Stata)
- `tab()`, `tab1()`, and `tab2()` for frequency tables (like `tab`, `tab1`, and `tab2` in Stata)
- `fre()`, `fre1()`, and `fre2()` for frequency tables with total rows and total columns (like `fre` in Stata) -->

## Installation

You can install the development version of statart like so:

```r
devtools::install_github("socimh/statart")
```

## Example

### Load the package

I highly recommend using `tidyverse` with `statart` for better performance.

```{r, warning=FALSE, message=FALSE}
library(statart)
library(tidyverse)
```

### codebook()

View the codebook of `lifeexp`.

```{r}
codebook(lifeexp)
```

### summ()

Summarise the numeric variables in `lifeexp`.

```{r, error=TRUE}
summ(lifeexp)
```

Not that `region` is a factor variable, so the mean and standard deviation of it may be meaningless.

### tab()

Tabulate a single variable:

```{r}
tab(starwars, sex)
```

`tab1()` tabulates variables one by one as a list, and `s_match()` can select variables in a stata style.


```{r}
tab1(starwars, s_match("*color"))
```

`.append` flattens the list into a tibble.

```{r}
tab1(starwars, s_match("*color"), .append = TRUE)
```

`tab2()` cross-tabulates two variables.

```{r}
tab2(starwars, sex, gender)
```


### fre()

`fre()` family functions simply add total rows (and total columns in `fre2()`) to their `tab()` counterparts.

```{r}
fre(starwars, sex)
```

## Code of Conduct

Please note that the statart project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
